Tomographic measurement of the intergalactic gas pressure through galaxy-tSZ cross-correlations

### 2019-10-16 notes/paper/paper.tex
sensitivity comment

      In particular, our model of the $y\times \delta_g$ cross-correlation is very sensitive to the width of the redshift distributions. This is because wider redshift distributions, which imply lower clustering amplitude, affect the amplitude of the galaxy auto-correlation, $\delta_g\times \delta_g$. At the same time, the $y$ auto-spectrum is almost insensitive to clustering; therefore the width only affects the $y\ times \delta_g$ cross-correlation in our analysis. We introduce an additional parameter, $w_z$, that stretches the support of the redshift distribution while preserving unit total probability. Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as
      \begin{equation}
        p(z)\propto p_{\rm fid}\left(\bar{z}+\frac{z-\bar{z}}{w_z}\right),
      \end{equation}
      where the proportionality constant is fixed by making sure that $p(z)$ integrates to unity. We make $w_z$ a free parameter that we marginalise over with a top-hat prior $0.8<w_z<1.2$. This prior is significantly larger than the actual expected uncertainty in the width of the redshift distributions. To be precise, we estimate that the parameters (e.g. Gaussian mean and variance) of the conditional photo-$z$ distribution $p(z|z_{\rm photo})$ used to calculate the true redshift distributions (Eq.\!~\ref{eq:nz_calc}), are known to the level of $1\%$. When propagated into an uncertainty on the width $w_z$ of $p(z)$, this corresponds to an uncertainty of the same order ($\sim0.9\%$). Thus, the margins of the assumed top-hat priors are wide enough to encompass any lack of precision in the number density distribution.

>>>>

      In particular, our constraints on $1-\bH$ are very sensitive to the width of the redshift distributions. This is because wider redshift distributions, which lead to lower projected clustering amplitudes, affect the galaxy auto-correlation, $\delta_g\times \delta_g$, while the $y\times\delta_g$ cross-correlation is almost insensitive to the width. We introduce an additional parameter, $w_z$, that stretches the support of the redshift distribution while preserving unit total probability. Concretely, given a fiducial distribution $p_{\rm fid}(z)$ with mean redshift $\bar{z}$, $w_z$ is implemented as
      \begin{equation}
        p(z)\propto p_{\rm fid}\left(\bar{z}+\frac{z-\bar{z}}{w_z}\right),
      \end{equation}
      where the proportionality constant is fixed by making sure that $p(z)$ integrates to unity. We make $w_z$ a free parameter that we marginalise over with a top-hat prior $0.8<w_z<1.2$. This prior is significantly larger than the actual expected uncertainty in the width of the redshift distributions. To be precise, we estimate that the parameters (e.g. Gaussian mean and variance) of the conditional photo-$z$ distribution $p(z|z_{\rm photo})$ used to calculate the true redshift distributions (Eq.\!~\ref{eq:nz_calc}), are known to the level of $1\%$. When propagated into an uncertainty on the width $w_z$ of $p(z)$, this corresponds to an uncertainty of the same order ($\sim0.9\%$). Thus, the margins of the assumed top-hat priors are wide enough to encompass any lack of precision in the number density distribution.
